\begin{section}{Recommendations}
  \begin{subsectionnobullet}{Leen Qasem}{Manager of Syrian Olympiads}{}{}
  \item
  I highly recommend Mr AmirReza for his outstanding work in preparing our international team for the IOI 2023. His deep expertise, coupled with his ability to simplify complex concepts, made a significant impact during our training camp.AmirReza tailored his approach to meet the needs of each participant, building confidence and fostering a strong problem-solving mindset.

Thanks to his guidance, our team developed both the technical skills and resilience required for success on the international stage. AmirReza is not only a skilled trainer but also an inspiring mentor. We’re grateful for his contribution to our IOI journey.

  \end{subsectionnobullet}
  \begin{subsectionnobullet}{Khalid Abdulnasser}{ACPC Cheif Judge}{}{}
  \item Amir worked with me in preparing the problem set for ACPC (Arab and Africa Programming Championship) for the years 2021 and 2023 for which I was the Chief Judge of the contest. 

Amir is an amazing problem setter and judge, the problems he brings are of top quality, and when he works on preparing a problem, his contributions are of the best quality I have ever seen. 

Amir can easily generate the hardest corner cases to find, and can reason about the most complicated algorithmic solutions, and those two qualities helped me prepare for these contests a great deal.

  \end{subsectionnobullet}
  
  \begin{subsectionnobullet}{Harshit Mehta}{Topcoder}{}{}
  \item Amir is somebody we could always rely on at Topcoder. He had all the passion and energy for the competitive programming community and he greatly contributed to it as well in the form of educational/fun problems, content and by always being available for helping and guiding other members. 

  \end{subsectionnobullet}
\end{section}
